---
title: "What the package does"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What the package does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753FALLsyrett)
```

# Introduction

This is my package for MATH-4753. It contains several functions from throughout the semester.

## Data

The package contains one data frame, fire. Fire contains two columns and 15 rows describing fire distance and damage.

## Function 1

The first function is mygetwd(). It merely gets the working directory. 
```{r}
mygetwd()
```

## Function 2

The second function is scatterhist(x, y, xlab, ylab). It takes in two data columns for X and Y and creates a scatter histogram with them. You can also label the x and y axis with xlab and ylab.
```{r}
scatterhist(fire$DISTANCE, fire$DAMAGE, xlab = "The x label", ylab = "the Y label")
```

## Function 3

The third function is mybin(iter, n, p). It runs a binomial experiment with size n and probability of success p iter times. It then produces a bar plot of the number of successes for each iteration. 
```{r}
mybin(iter = 100, n = 10, p = 0.5)
```

## Function 4

The fourth function is myncurve(mu, sigma, a). It produces a curve with the lower tail shaded and returns the calculated lower tail probability. 
```{r}
myncurve(0,1,0.05)
```

## Function 5

The fifth function is myntickets(N, gamma, p). This produces a solution for the airline overbooking problem.
```{r}
myntickets()
```

## Function 6

The sixth function is myboot2(iter, x, fun, alpha, cx, ...). This is a bootstrap moment generating function.
```{r}
myboot2(x=fire$DAMAGE)
```



